A Sample {\ttlit ACM} SIG Proceedings Paper in LaTeX Format\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}

### 2014-03-07 paper/draft.tex
First Revision

In addition, MH inherits the concept of micro-kernel to implement different ``personalities''. Those ``personalities'' are concretely a set of ``processes'' handling specific functions running in user-space. As those functions are implemented outside the kernel, they are not unique but they are changeable and could coexist at the same time. This feature was seen with interest because of the possibility to move some virtualization-related from the kernelspace to user-space and to strictly separate piece of software executed for different users. This extraction process drives to a more solid platform, considering that user-space crashes are generally not fatal for the whole system.  A possible example, that will be analyzed in next section, is the user-space VMM component of Nova, Vancouver, that resides in user-space \cite{nova}.

>>>>

In addition, MH inherits the concept of micro-kernel to implement different ``personalities''. Those ``personalities'' are concretely a set of ``processes'' handling specific functions running in user-space. As those functions are implemented outside the kernel, they are not unique but they are changeable and could coexist at the same time. This feature was seen with interest because of the possibility to move some virtualization-related from the kernel space to user-space and to strictly separate piece of software executed for different users. This extraction process drives to a more solid platform, considering that user-space crashes are generally not fatal for the entire system integrity.  A possible example, that will be analyzed in next section, is the user-space VMM component of Nova, Vancouver, that resides in user-space \cite{nova}.
